Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE)

### 2014-02-04 WSSSPE1_report/WSSSPE1_summary_report.tex
org change - removed agenda section started to change some URLs to cites fixed some todos

\note{papers and presentations should be references - URLs perhaps can just be footnotes for now, but may want to think about this again.}

@@

\section{Workshop Process}

WSSSPE1 was organized in collaboration of the relatively small group of \todo{how many} organizers and
a larger peer-review committee consisting of \todo{how many members}. This committee had early influence on the organization,
e.g., on the specific call for papers.

@@

58 submissions were received, and almost all submitters used either 
arXiv\footnote{\url{http://arxiv.org}} or 
figshare\footnote{\url{http://figshare.com}} to self-publish their papers.

@@

\section{Agenda}

The workshop consisted of two keynote presentations and three panels/discussion sessions. The panels 
were organized based on a classification of the workshop submissions into three categories, following 
the themes of the call for papers as modified by the areas of the submissions. Four \todo{Is it five?} representatives from 
each submission categories were appointed as panelists, to discuss the papers in that category.

@@

@@

He talked about grant schemes of relevance in the U.S., particularly with regard to technology transfer.\footnote{\url{http://www.nsf.gov/pubs/policydocs/pappguide/nsf09_1/gpg_2.jsp\#IID2}} \footnote{\url{http://www.nsf.gov/eng/iip/sbir/}} \todo{change at least first to cite}

@@

\subsection{Scientific Software and the Open Collaborative Web}

@@

\section{Illustrative use-cases}

@@

>>>>

\note{papers and presentations and URLs should be references - see figshare-web in .bib file for URL style example}

@@

\section{Workshop Process and Agenda}

WSSSPE1 was organized in collaboration of the relatively small group of five organizers and
a larger peer-review committee with 36 members. This committee had early influence on the organization,
e.g., on the specific call for papers.

@@

58 submissions were received, and almost all submitters used either 
arXiv~\cite{arXiv-web} or 
figshare~\cite{figshare-web} to self-publish their papers.

@@

The workshop itself consisted of two keynote presentations and the three panels/discussion sessions. The panels 
were organized based on a classification of the workshop submissions into three categories, following 
the themes of the call for papers as modified by the areas of the submissions. Three to four representatives from 
each submission category were appointed as panelists, and assigned to read a subset of the paper in that category and then discuss them in the panel.

@@

The WSSSPE1 workshop began with two keynote presentations.

@@

He talked about grant schemes of relevance in the U.S., particularly with regard to technology transfer.\footnote{\url{http://www.nsf.gov/pubs/policydocs/pappguide/nsf09_1/gpg_2.jsp\#IID2}} \footnote{\url{http://www.nsf.gov/eng/iip/sbir/}}

@@

\subsection{Scientific Software and the Open Collaborative Web, Arfon Smith}

@@

\section{Illustrative Use Cases}

@@

\note{Dan: do we need this section?  I think there's some overlap between this and the discussion in the Developing and Support Software section.  Or perhaps this should go in the cross-cutting issues section?}
